\LARGE \bf Approximately Orchestrated Routing and Transportation Analyzer:\\ Large-scale Traffic Simulation for Autonomous Vehicles

### 2012-03-15 papers/itsc_2012/final.tex
adding houston results, WIP

The last policy tested is an autonomous reservation policy inspired by AIM
\cite{JAIR08-dresner}. This policy groups agents with compatible turns together,
allowing new agents to join existing groups. To prevent one heavy direction of
traffic from hogging the intersection indefinitely, a timeout preemptively
cycles through reservations.

@@

\begin{figure}[h]
  \centering \includegraphics[width=\linewidth]{avg_lag_agent_atx.png}
  \caption{The distribution of average delay reveals that traffic signals can
           cause the most lag.}
  \label{fig:avg_lag}
  \vspace{-10pt}
\end{figure}

@@

\begin{figure}[h]
  \centering \includegraphics[width=\linewidth]{agent_cnt_atx.png}
  \caption{Autonomous reservations outperform stop signs, and traffic signal
           gridlocked.}
  \label{fig:agent_cnt}
  \vspace{-10pt}
\end{figure}

>>>>

The last policy tested is an autonomous reservation policy inspired by AIM
\cite{JAIR08-dresner}. Because agents explicitly communicate with intersections
to schedule their turn, this policy is only suitable for autonomous drivers.
This policy groups agents with compatible turns together, allowing new agents to
join existing groups. To prevent one heavy direction of traffic from hogging the
intersection indefinitely, a timeout preemptively cycles through reservations.

@@

\begin{figure*}[h]
  \centering
  \subfloat[Average delay in Austin]{
    \includegraphics[width=0.5\linewidth]{avg_lag_agent_atx.png}
    \label{fig:avg_lag_atx}
  }
  \subfloat[Average delay in Houston]{
    \includegraphics[width=0.5\linewidth]{avg_lag_agent_houston.png}
    \label{fig:avg_lag_houston}
  }
\end{figure*}
\begin{figure*}[h]
  \subfloat[Number of agents driving in Austin]{
    \includegraphics[width=0.5\linewidth]{agent_cnt_atx.png}
    \label{fig:agent_cnt_atx}
  }
  \subfloat[Number of agents driving in Houston]{
    \includegraphics[width=0.5\linewidth]{agent_cnt_houston.png}
    \label{fig:agent_cnt_houston}
  }
  \caption{Autonomous reservations outperform stop signs and traffic signals in
           these experiments.}
  %\vspace{-10pt}
\end{figure*}

@@
